Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-22 tex/paper1/paper1.tex
edits
edits to the paper, and adding in posterior predictive T_SSE test

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a \PL\ behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed \PL\ \PS\ can be
formed by summing a distribution of exponentially decaying emission
events along the line of sight.  This is consistent with the notion
that the solar atmosphere is heated everywhere by small energy
deposition events.
\end{abstract}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figure
\ref{fig:fit171193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

\section{Discussion}
The presence of a \PL\ Fourier spectrum in coronal emission poses
questions about how that emission is formed.  The \PL\ \PS\ also has
implications for the detection of narrow frequency band oscillations
against such a background emission, which is the purview of coronal
seismology.  We discuss these two topics in the sections below.

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013}, PyMC
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific Python
stack for providing data preparation, manipulation, analysis and
display packages.  This work was supported by the NASA award number????

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).

>>>>

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a \PL\ behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
The implications of this discovery to the field of coronal seismology
and automated detections of oscillations is discussed.  Further, it is
shown that the observed \PL\ \PS\ can be formed by summing a
distribution of exponentially decaying emission events along the line
of sight.  This is consistent with the notion that the solar
atmosphere is heated everywhere by small energy deposition events.

\end{abstract}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions, and compared to
decide which model best describes the data.  The model comparison
process is described in Section \ref{ssec:compare}.

\subsection{Comparing spectral models}\label{ssec:compare}
Deciding which model best fits the data is achieved using a model
comparison process based on the work of \cite{2010MNRAS.402..307V}.
In the first part of this work, two models of the background Fourier
power spectrum from XMM-Newton observations of highly variable Seyfert
1 galaxies are compared to find which one best describes the
background spectrum.  The comparison process is as follows.

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  Table \ref{tab:parameters} shows the fitted parameter values
and an error estimate for model $M_{2}$.  For details on the fitting
procedure, see Section \ref{sec:app:ind}.

\section{Discussion}
The presence of a \PL\ \PS\ has implications for the detection of
narrow frequency band oscillations against such a background emission,
for both non-automated and automated methods.  These are discussed in
Sections \ref{ssec:corseis} and \ref{sec:oscdetect}.  Further, the
\PL\ Fourier spectrum in coronal emission poses questions about how
that emission is formed.  A hypothesis regarding the formation of this
power law spectrum is presented in Section \ref{ssec:nplps}.

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific
Python stack for providing data preparation, manipulation, analysis
and display packages.  This work was supported by NASA award
NNX13AE03G S01 funded through NASA ROSES NNH12ZDA001N-SHP.

@@

\section{Details of the model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).
